Evaluation of performances

### 2021-06-21 analysis/eval-performance.Rmd
upd feature sel table caption

table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. \texttt{#} denotes the absolute number of features selected and 'Features (\texttt{%})' refers to the percentage relative to the overall features available (7675). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 0, 2)
  )

>>>>

table4 <- df_tbl %>%
  xtable::xtable(
    type = "latex",
    caption = "Selected feature portions during tuning for the best performing learner-filter settings (SVM Relief, RF Relief, XGBoost CMIM) across folds for task HR-NRI-VI, sorted by plot name. \\texttt{#} denotes the absolute number of features selected and 'Features (\\texttt{%})' refers to the percentage relative to the overall features available (7675). Results were estimated in a separate model tuning step, not within the main cross-validation comparison.",
    label = "tab:tune-perc-sel-features",
    digits = c(0, 0, 0, 5, 0, 2)
  )
